### 2020-04-21 final_report/data.tex
add model description section

Data

\subsection{Feature Description}
\label{sec:feature-description}

TODO
\begin{enumerate}
	\item about single sphere OpenMC sim
	\item parameter listing
	\item continuous vs discrete features
	\item discrete embedding
\end{enumerate}

>>>>

The initial step of our work is the study of the existing MC TBR model and its
behaviour. Following the examination of its features (simulation parameters), we
present efficient means of evaluating this model on large sets of points in HPC
environment, preprocessing techniques designed to adapt collected datasets for
surrogate modelling, and our attempts at feature space reduction to achieve the
lowest possible number of dimensions.

\subsection{Expensive Model Description}
\label{sec:expensive-model-description}

The MC TBR model that we understand to be the expensive function for our
surrogate modelling is fundamentally a Monte Carlo simulation based on the OpenMC
framework. At input the software expects a set of 19~parameters, discrete and
continuous, that are fully listed in~\cref{tbl:params}. Following a brief period of
time (usually on the order of tens of seconds), during which a fixed number of events is simulated, the software outputs the
mean and the standard deviation of the TBR aggregated over the simulated run. The
former of these two outputs we accept to be the output TBR value that is subject
to approximation.

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Parameter name & Type & Domain & Description\\
		\midrule
		TODO & TODO & TODO & TODO\\
		\bottomrule
		\end{tabular}
	}
	\caption{Input parameters supplied to the MC TBR simulation.}
	\label{tbl:params}
\end{table}

In our work, we often reference TBR points or samples. These are simply vectors
in the feature space generated by Cartesian product of domains of all
features---parameters from~\cref{tbl:params}.

Since most surrogate models
that we employ assume overall continuous inputs, we take steps to unify our
feature interface in order to attain this property. In particular, we eliminate
discrete features by embedding each such feature into a finite multitude of
continuous features using standard one-hot encoding. This option is available to
us since discrete domains that generate our feature space are finite in
cardinality and relatively small in size. And while it renders all features continuous, the
modification comes at the expense of increasing the dimensionality of the
feature space, which is comprised of 27 features from this point on.
